A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-10-07 latex/main.tex
Updates from Overleaf

% Multiple-breakpoint recombinants
% https://github.com/jeromekelleher/sc2ts-paper/issues/379
Ten Pango X lineages present in the Viridian v04 dataset
were not integrated into the ARG
due to high HMM costs and/or insufficient sample support,
but their samples were matched against the ARG during inference.
Table~\ref{tab:absent_pango_x} summarizes
the HMM matching results of these Pango X lineages.
All were identified as recombinants by sc2ts, except XBL
for which the evidence for recombination
supporting the suggested rightmost parent
involves only three informative sites,
which fall below our threshold of detection.
These results demonstrate that sc2ts can detect
recombinants with multiple breakpoints (XAY, XBC, and XBT).
The recombination patterns of these Pango X lineages
can be complex; exploring how to integrate such recombinants
should an important direction for future work.

>>>>

% Multiple-breakpoint recombinants
% https://github.com/jeromekelleher/sc2ts-paper/issues/379
Ten Pango X lineages present in the Viridian v04 dataset
were not integrated into the ARG
due to high HMM costs and/or insufficient sample support,
but their samples were matched against the ARG during inference.
Table~\ref{tab:absent_pango_x} summarizes
the HMM matching results of these Pango X lineages.
All were identified as recombinants by sc2ts, except XBL.
The evidence for recombination
supporting the suggested rightmost parent
involves only three informative sites,
which fall below our threshold of detection.
These results demonstrate that sc2ts can detect
recombinants with multiple breakpoints (XAY, XBC, and XBT).
The recombination patterns of these Pango X lineages
can be complex; exploring how to integrate such recombinants
should an important direction for future work.
